\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-07-28 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

Additionally, in the Chinese real estate market, brokerages still operate on a bilateral agency model, where sellers need to choose the agency that can help them sell their home in the fastest time and for the highest price possible for the transaction. However, due to the asymmetric information inherent in the real estate market, sellers face challenges in effectively informing and matching with potential buyers. In a perfectly competitive market, sellers would be indifferent in their choice of real estate agents. Nonetheless, as the market trends toward increased monopolization, sellers confront a dichotomous decision: engage a larger brokerage firm, which, despite higher fees, offers the potential for expedited transactions, or opt for a smaller brokerage with lower fees but potentially less efficient transaction facilitation.

@@

>>>>

Additionally, in the Chinese real estate market, brokerages still operate on a bilateral agency model, where sellers need to choose the agency that can help them sell their home in the fastest time and for the highest price possible for the transaction. However, due to the asymmetric information inherent in the real estate market, sellers face challenges in effectively informing and matching with potential buyers. In a perfectly competitive market, sellers would be indifferent in their choice of real estate agents. Nonetheless, as the market trends toward increased monopolistic competition, sellers confront a dichotomous decision: engage a larger brokerage firm, which, despite higher fees, offers the potential for expedited transactions, or opt for a smaller brokerage with lower fees but potentially less efficient transaction facilitation.

@@

\subsection{Mechanism Design} \label{subsec:mechanism_network_design}

In the real estate market, real estate is not a homogeneous good, and the market is characterized by a large number of firms with no significant barriers to entry. Traditional economic theory suggests that such a market, characterized by substantial competition, numerous firms, and low market concentration, is consistent with real-world observations. For example, Lianjia's offline stores account for less than 5\% of the total, yet Lianjia handles about 20\% of the national transactions. In addition, many well-known agencies, such as Woaiwojia and Centaline Property Agency, operate in this market, indicating a monopolistic competitive environment.

However, when looking at local segmented markets, the monopolistic competition model seems less applicable. In local markets, surrounding neighborhoods share similar community characteristics and public resources. Especially in China's real estate market, most properties are apartments, where the inherent differences between properties are minimal, making them relatively homogeneous goods. In addition, local real estate markets have no barriers to entry or exit, closely resembling perfect competition. From a cost perspective, the real estate market has undergone platform mediated reforms, where data resources have zero marginal cost characteristics and operating costs decrease as the user base expands, suggesting characteristics of a natural monopoly. Under these conditions, the operating position of firms differs significantly from that in a monopolistically competitive market. Due to network effects, an increase in the number of branches of a dominant real estate agency attracts more users, which in turn attracts more real estate listings. This positive feedback loop reinforces the dominant position of firms like Lianjia, leading to the formation of oligopolistic firms. These oligopolistic firms can further maintain their dominant market positions. Thus, even in the absence of barriers to entry and despite the presence of many competing firms, their operations can resemble those of a full monopoly.

As our empirical results show, Lianjia's strategy has significantly enhanced its network strength within segmented markets. From this perspective, the enhancement of network effects further drives the market toward an oligopolistic competitive structure. Moreover, with the development of online platforms and new technologies, such as Lianjia's latest VR home viewing technology, these network effects are gradually shifting from local networks to a global network. As a result, this development is shaping the overall market into an oligopolistic competition model on a larger scale.
